---
title: "Exercises"
author: "Tim Dennis"
date: "October 2, 2016"
output: 
  html_document: 
    toc: yes
---

```{r setup, include=FALSE}
library(rentrez)
knitr::opts_chunk$set(echo = TRUE)
```

## Excercises 
### 1: DOI Search

Given the following DOI, use pubmed database to fill in the following information: 

**DOI: 10.1111/nyas.13259**

1. TITLE: 
2. AUTHORS: 
3. SOURCE
4. PUBDATE: 

###2: Keyword search 

Search entrez for a topic covered by this class.

###3: Qualifiers 

Pick a data base in entrez and find the available qualifiers `entrez_db_searchable("sra")`. You can look up the search fields and qualifiers here: <https://www.ncbi.nlm.nih.gov/entrez/query/static/help/Summary_Matrices.html#Search_Fields_and_Qualifiers>. Using the qualifiers perform a search on a topic of your choice. Explore the object that R returns. 


###4: Mesh Search

Now, perform a Mesh search. The example we used in class was: 

```{r, mesh}
entrez_search(db   = "pubmed",
              term = "(vivax malaria[MeSH]) AND (folic acid antagonists[MeSH])")
```

Try different Mesh terms in pubmed. You can look up Mesh terms here <http://www.ncbi.nlm.nih.gov/mesh> or query the `Mesh` databse with the term: `entrez_search(db="mesh", term =...)`.

##Answers

###1: DOI Search
```{r answer1}
ex1_paper <- entrez_search(db="pubmed", term="10.1111/nyas.13259[doi]")
ex1_summary <- entrez_summary(db="pubmed", ex1_paper$ids)
ex1_summary$title
ex1_summary$authors
ex1_summary$source
ex1_summary$pubdate
```

###2. Keyword search

```{r searchids_2, eval=FALSE}
another_r_search <- entrez_search(db="pubmed", term="Natural Language Processing", retmax=40)
another_r_search
```

###3: Qualifiers: 

```{r, Tt3-qual}
entrez_search(db="sra",
              term="(Tetrahymena thermophila[ORGN] OR Tetrahymena borealis[ORGN]) AND 2013:2015[PDAT]",
              retmax=0)
```

###4: Mesh search

```{r, mesh-ans}
entrez_search(db   = "pubmed",
              term = "(vivax malaria[MeSH]) AND (folic acid antagonists[MeSH])")
```