---
title: 'MED 264: R Homework'
author: "Tim Dennis"
date: "10/4/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Homework Instructions:** 

1. Download the word version of this [document](homework-into-r.docx). You may also write a R script with the answers. 
2. Add your answers to the document. 
3. "Save as" your file as \<yourname\>-med264-rhomework.docx. 
4. Bring to class on Thursday. 

## 1. Vector Types

Look at the help for the c function. What kind of vector do you expect you will create if you evaluate the following:

```{r eval=FALSE}
c(1, 2, 3)
c('d', 'e', 'f')
c(1, 2, 'f')
```

## 2. Making a vector

Start by making a vector with the numbers 1 through 26. Multiply the vector by 2, and give the resulting vector names A through Z (hint: there is a built in vector called LETTERS).

## 3. Addressing objects in a data.frame


There are several subtly different ways to call variables, observations and
elements from data.frames:

- `cats[1]`
- `cats[[1]]`
- `cats$coat`
- `cats`["coat"]
- `cats[1, 1]`
- `cats[, 1]`
- `cats[1, ]`

> Load the data into R: 
>
> `cats <- read.csv('https://raw.githubusercontent.com/jt14den/med264/gh-pages/data/feline-data.csv')`
>
>Try out these examples and explain what is returned by each one.
>
> *Hint:* Use the function `typeof()` to examine what is returned in each case.

## 4. Subsetting a vector

Given the following code:


```{r}
x <- c(5.4, 6.2, 7.1, 4.8, 7.5)
names(x) <- c('a', 'b', 'c', 'd', 'e')
print(x)
```

>1. Write a subsetting command to return the values in x that are greater than 4 and less than 7.

## 5. Write a function in R

Write a function called `kelvin_to_celsius` that takes a temperature in Kelvin
and returns that temperature in Celsius

Hint: To convert from Kelvin to Celsius you subtract 273.15