---
title: "rentrez Searching Metadata"
date: "10/5/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

* Taken from Ted Hart's workshop on ROpenscience at SIO14 

<!--
Searching metadata
========================================================

We offer several ways to search metadata, `rmetadata`, and `rentrez`

```{r}
#library(devtools)
#install_github("rentrez","ropensci")
#install_github("rmetadata","ropensci")
#install_github("rcrossref","ropensci")
#install_github("raltmetric","ropensci")
#install_github("alm","ropensci")
#install_github("rcrossref","ropensci")
#install.packages("tm")
#install.packages("wordcloud")


```

Let's start by searching for terms with rmetadata from the crossref database.

```{r search with rmetadata}
options(stringsAsFactors=F)
#library(rcrossref)
#library(rmetadata)
# library(rentrez)
# library(reshape2)
# library(ggplot2)
#toxo <- crossref_search(q = "toxoplasmosis")

## We can also extend these to search by year, and change the number of records we have

# toxo2 <- crossref_search(q = "toxoplasmosis", rows = 100, year = 2010)
# 
# 
# ### we can view these records 
# 
# toxo2[34,]$doi
# toxo2[34,]$fullCitation
# 
# ### Doi's come back with http appended, let's strip it off
# toxo2$doi_nohttp <- gsub("http://dx.doi.org/","",toxo2$doi)
# 
# #We can also see the full citation
# print(crossref_citation("10.1016/j.cub.2013.11.014"), style="Bibtex")
# print(crossref_citation(toxo2$doi_nohttp[55]))
# 

```
-->

## Search and plot trendy topics in genetics example
* We can also search pubmed abstracts with the [`rentrez`](https://github.com/ropensci/rentrez) package

* you can also use entrez to search pubmed and the EUtils API allows you to limit searches by the year in which the paper was published. 

* For example we can find the trendiest -omics going around (this has quite a lot of repeated searching, so you want to run your own version be sure to do it in off peak times).

* Let's start by making a function that finds the number of records matching a given search term for each of several years (using the mindate and maxdate terms from the Eutils API):

### Load packages in RStudio 
```{r}
library(rentrez)
library(reshape2)
library(ggplot2)
```

### Create a function
```{r}
papers_by_year <- function(years, search_term){
  return(sapply(years, function(y) entrez_search(db="pubmed", term = search_term, mindate=y, maxdate=y, retmax=0)$count))
}
```

* With that we can fetch the data for each term and, by searching with no term, find the total number of papers published in each year:

```{r}
years <- 1990:2015
total_papers <- papers_by_year(years, "")
omics <- c("genomic", "epigenomic", "metagenomic", "proteomic", "transcriptomic", "pharmacogenomic", "connectomic" )
trend_data <- sapply(omics, function(t) papers_by_year(years, t))
trend_props <- trend_data/total_papers
```

* That's the data, ready for plot:

```{r}
trend_df <- melt(data.frame(years, trend_props), id.vars="years")
p <- ggplot(trend_df, aes(years, value, colour=variable))
p + geom_line(size=1) + scale_y_log10("number of papers")
```



### Full code
<!--
```{r}
dmagna <- entrez_search(db="pubmed",term="Daphnia magna", retmax=1000)
```
-->

```{r}
papers_by_year <- function(years, search_term){
            return(sapply(years, function(y) entrez_search(db="pubmed",term=search_term, mindate=y, maxdate=y, retmax=0)$count))
        }

years <- 1990:2011
total_papers <- papers_by_year(years, "")
omics <- c("genomic", "epigenomic", "metagenomic", "proteomic", "transcriptomic", "pharmacogenomic", "connectomic" )
trend_data <- sapply(omics, function(t) papers_by_year(years, t))
trend_props <- data.frame(trend_data/total_papers)
trend_props$years <- years

trend_df <- melt(as.data.frame(trend_props), id.vars="years")
p <- ggplot(trend_df, aes(years, value, colour=variable)) 
p + geom_line(size=1) + scale_y_log10("number of papers")


```

